# Data From MT-Cars

Example of literate programming with the MT-cars data. Above we have added a title with markdown, here we are adding som text, and below there is a horizontal line.

***

## Introduction

Above there is a subtitle. Next, we will add an R code chunk. In order to get and process the data, we need the following libraries:
```{r get_libraries}
library(dplyr)
```
This code chunk loads the dply library.

## Data Processing

Let's do some work with the MT-cars data and display the result. First, we subset the data to only include cars with more than 6 cylinders, and then we display the result.
```{r subsetting_data}
mtcars_subset <- subset(mtcars, mtcars$cyl > 6)
mtcars_subset
```
## Graphics

Graphics can easily be included in the report. Using the base barplot function: 

```{r bar_chart_mtcars, fig.cap = "Figure 1: MPG for cars with more that 6 cylinders", fig.width=10, fig.height=4}
par(mar=c(10,4,1,1),las=3)
barplot(mtcars_subset$mpg, names.arg=row.names(mtcars_subset),
     col=rainbow(15), ylab = "Miles per gallon", 
     ylim = c(0,max(mtcars_subset$mpg)))
```

